---
title: "Treatment Analyses"
author: "Crystal Lewis"
date: "1/21/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(haven)
library(knitr)
library(furniture)
library(jtools)
library(kableExtra)
library(ggplot2)
```

```{r, echo=FALSE}
#Read in data and drop cases with na
#Recode categorical vars
MARS<-read_sav("TreatmentData.sav")%>%mutate(Race=as.numeric(Race),
                                                        Female=as.numeric(Female),
                                                        Age=as.numeric(Age),
                                                        Group=as.numeric(Group))
MARS<-MARS%>%drop_na()

```

```{r, echo=FALSE}
#Recode Race and Gender
MARS<-MARS%>%mutate(Race= recode_factor(Race, `0`='White', `2` = 'Non-White',
                                        `1`='Non-White'))

MARS<-MARS%>%mutate(Gender= recode_factor(Female, `0`='Male', `1`='Female'))

MARS<-MARS%>%mutate(GradeLevel=recode_factor(Age, `1`='Elementary', `2`='Secondary'))

MARS<-MARS%>%mutate(Group=recode_factor(Group, `0`='Control', `1`='Treatment'))
```

## Summary table for categorical variables
```{r, echo=FALSE, warning=FALSE, message=FALSE}
MARS2<-MARS%>%select("Race", "Gender", "GradeLevel", "Group",
                     "GSET1_TRS":"SchoolProbsT1_TRS", "EmotionalSympT1_SRP":
                       "SchoolProbsT1_SRP")

MARS2%>%group_by(Group)%>%table1(Race, Gender, GradeLevel,
                  format_number = TRUE, 
                  test = TRUE,
                 output="pandoc")
```

## Summary table for baseline BASC variables
```{r, echo=FALSE, warning=FALSE, message=FALSE}
MARS2%>%group_by(Group)%>%table1(GSET1_TRS,
AdaptSkillsT1_TRS,
BehavioralSymT1_TRS,
ExternalizingT1_TRS,
InternalizingT1_TRS,
SchoolProbsT1_TRS,
EmotionalSympT1_SRP,
InternalizingT1_SRP,
PersonalAdjustT1_SRP,
SchoolProbsT1_SRP,
                  format_number = TRUE, 
                  test = TRUE,
                 output="pandoc")
```

```{r, echo=FALSE, eval=FALSE}
T<-tableone::CreateTableOne(data=MARS2, strata = "Group", test=FALSE)

print(T,showAllLevels=TRUE,output="html")
```


```{r, echo=FALSE}
#Create scaled outcomes

MARS$ODR2scale<-scale(MARS$ODR2)

MARS$OSS2scale<-scale(MARS$OSS2)

MARS$ELA2scale<-scale(MARS$ELA2)

MARS$Math2scale<-scale(MARS$Math2)

MARS$Minor2scale<-scale(MARS$Minor2)

MARS$GSET2_TRSscale<-scale(MARS$GSET2_TRS)

MARS$AdaptSkillsT2_TRSscale<-scale(MARS$AdaptSkillsT2_TRS)

MARS$BehavioralSymT2_TRSscale<-scale(MARS$BehavioralSymT2_TRS)

MARS$ExternalizingT2_TRSscale<-scale(MARS$ExternalizingT2_TRS)

MARS$InternalizingT2_TRSscale<-scale(MARS$InternalizingT2_TRS)

MARS$SchoolProbsT2_TRSscale<-scale(MARS$SchoolProbsT2_TRS)

MARS$EmotionalSympT2_SRPscale<-scale(MARS$EmotionalSympT2_SRP)

MARS$InternalizingT2_SRPscale<-scale(MARS$InternalizingT2_SRP)

MARS$PersonalAdjustT2_SRPscale<-scale(MARS$PersonalAdjustT2_SRP)

MARS$SchoolProbsT2_SRPscale<-scale(MARS$SchoolProbsT2_SRP)
```

## School Outcome Models

### ODR
```{r, echo=FALSE}

lm1scale<-lm(ODR2scale~ Gender+ Race+ ODR1 + GradeLevel+ Group,data=MARS)

lm1<-lm(ODR2~ Gender+ Race+ ODR1 + GradeLevel+ Group,data=MARS)

export_summs(lm1scale,lm1, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### OSS
```{r, echo=FALSE}
lm2scale<-lm(OSS2scale~ Gender+ Race+ OSS1 + GradeLevel+ Group,data=MARS)

lm2<-lm(OSS2~ Gender+ Race+ OSS1 + GradeLevel+ Group,data=MARS)

export_summs(lm2scale, lm2,model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### ELA
```{r, echo=FALSE}

lm3scale<-lm(ELA2scale~ Gender+ Race+ ELA1+ GradeLevel+ Group,data=MARS)

lm3<-lm(ELA2~ Gender+ Race+ ELA1+ GradeLevel+ Group,data=MARS)

export_summs(lm3scale,lm3,model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Math
```{r, echo=FALSE}
lm4scale<-lm(Math2scale~ Gender+ Race+ Math1 + GradeLevel+ Group,data=MARS)

lm4<-lm(Math2~ Gender+ Race+ Math1 + GradeLevel+ Group,data=MARS)

export_summs(lm4scale,lm4,model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### MinorODR
```{r, echo=FALSE}

lm5scale<-lm(Minor2scale~ Gender+ Race+ Minor1 + GradeLevel+ Group,data=MARS)

lm5<-lm(Minor2~ Gender+ Race+ Minor1 + GradeLevel + Group,data=MARS)

export_summs(lm5scale,lm5,model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Graph of school outcomes
```{r, echo=FALSE}
plot_summs(lm2scale, lm3scale, lm1scale, lm4scale, lm5scale,
           coefs=c("Treatment"="GroupTreatment"),
           model.names=c("OSS", "ELA", "ODR", "Math", "Minor ODR"),
           colors=c("black","black", "black", "black", "black"), 
           point.shape=TRUE,legend.title="Student School Outcome")+ coord_flip()+
  ylab("Largest to Smallest Effect Size")

```

## SRP Models

### Emotional Symptoms
```{r, echo=FALSE}
lm6scale<-lm(EmotionalSympT2_SRPscale~ Gender+ Race+ EmotionalSympT1_SRP + GradeLevel+ Group,data=MARS)

lm6<-lm(EmotionalSympT2_SRP~ Gender+ Race+ EmotionalSympT1_SRP + GradeLevel+ Group,data=MARS)

export_summs(lm6scale,lm6, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Internalizing
```{r, echo=FALSE}
lm7scale<-lm(InternalizingT2_SRPscale~ Gender+ Race+ InternalizingT1_SRP + GradeLevel+ Group,data=MARS)

lm7<-lm(InternalizingT2_SRP~ Gender+ Race+ InternalizingT1_SRP + GradeLevel+ Group,data=MARS)

export_summs(lm7scale,lm7, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Personal Adjustment
```{r, echo=FALSE}
lm8scale<-lm(PersonalAdjustT2_SRPscale~ Gender+ Race+ PersonalAdjustT1_SRP + GradeLevel+ Group,data=MARS)

lm8<-lm(PersonalAdjustT2_SRP~ Gender+ Race+ PersonalAdjustT1_SRP + GradeLevel+ Group,data=MARS)

export_summs(lm8scale,lm8, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```


### School Problems
```{r, echo=FALSE}
lm9scale<-lm(SchoolProbsT2_SRPscale~ Gender+ Race+ SchoolProbsT1_SRP + GradeLevel+ Group,data=MARS)

lm9<-lm(SchoolProbsT2_SRP~ Gender+ Race+ SchoolProbsT1_SRP + GradeLevel+ Group,data=MARS)

export_summs(lm9scale,lm9, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```


### Graph of SRP outcomes
```{r, echo=FALSE}
plot_summs(lm9scale, lm8scale, lm6scale, lm7scale,
           coefs=c("Treatment"="GroupTreatment"),
           model.names=c("School Problems", "Personal Adjustment",
                          "Emotional Symptoms",  "Internalizing"),
           colors=c("black", "black", "black", "black"), 
           point.shape=TRUE,legend.title="BASC SRP Outcome")+ coord_flip()+
  ylab("Largest to Smallest Effect Size")
```


## TRS Models

### GSE
```{r, echo=FALSE}
lm10scale<-lm(GSET2_TRSscale~ Gender+ Race+ GSET1_TRS + GradeLevel+ Group,data=MARS)

lm10<-lm(GSET2_TRS~ Gender+ Race+ GSET1_TRS + GradeLevel+ Group,data=MARS)

export_summs(lm10scale,lm10, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Adapt Skills
```{r, echo=FALSE}
lm11scale<-lm(AdaptSkillsT2_TRSscale~ Gender+ Race+ AdaptSkillsT1_TRS + GradeLevel+ Group,data=MARS)

lm11<-lm(AdaptSkillsT2_TRS~ Gender+ Race+ AdaptSkillsT1_TRS + GradeLevel+ Group,data=MARS)

export_summs(lm11scale,lm11, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Behavioral Symptoms
```{r, echo=FALSE}
lm12scale<-lm(BehavioralSymT2_TRSscale~ Gender+ Race+ BehavioralSymT1_TRS + GradeLevel+ Group,data=MARS)

lm12<-lm(BehavioralSymT2_TRS~ Gender+ Race+ BehavioralSymT1_TRS + GradeLevel+ Group,data=MARS)

export_summs(lm12scale,lm12, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Externalizing
```{r, echo=FALSE}
lm13scale<-lm(ExternalizingT2_TRSscale~ Gender+ Race+ ExternalizingT1_TRS + GradeLevel+ Group,data=MARS)

lm13<-lm(ExternalizingT2_TRS~ Gender+ Race+ ExternalizingT1_TRS + GradeLevel+ Group,data=MARS)

export_summs(lm13scale,lm13, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Internalizing
```{r, echo=FALSE}
lm14scale<-lm(InternalizingT2_TRSscale~ Gender+ Race+ InternalizingT1_TRS + GradeLevel+ Group,data=MARS)

lm14<-lm(InternalizingT2_TRS~ Gender+ Race+ InternalizingT1_TRS + GradeLevel+ Group,data=MARS)

export_summs(lm14scale,lm14, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### School Problems
```{r, echo=FALSE}
lm15scale<-lm(SchoolProbsT2_TRSscale~ Gender+ Race+ SchoolProbsT1_TRS + GradeLevel+ Group,data=MARS)

lm15<-lm(SchoolProbsT2_TRS~ Gender+ Race+ SchoolProbsT1_TRS + GradeLevel+ Group,data=MARS)

export_summs(lm15scale,lm15, model.names = c("Standardized","Unstandardized"),
             coefs=c("Treatment"="GroupTreatment"))
```

### Graph of TRS outcomes
```{r, echo=FALSE}
plot_summs(lm15scale,lm13scale, lm14scale,lm12scale, lm11scale, lm10scale,
           coefs=c("Treatment"="GroupTreatment"),
           model.names=c("School Problems","Externalizing",
                         "Internalizing", 
                         "Behavioral Symptoms","Adaptation Skills", 
                         "GSE"),
           colors=c("black", "black", "black", 
                    "black", "black", "black"), 
           point.shape=TRUE,legend.title="BASC TRS Outcome")+ coord_flip()+
  ylab("Largest to Smallest Effect Size")
```